R for Clinical Study Reports and Submission

### 2022-08-12 tlf-assemble.Rmd
enable tmporary solution for `rtf_assemble`.

```{r}
tlf_path <- c(
  "tlf/tlf_disp.rtf",  # Disposition Table 
  "tlf/tlf_eff.rtf",   # Efficacy Table
  "tlf/tlf_km.rtf"     # KM Plot 
)
```

@@

The `r2rtf::rtf_assemble()` function allow you to combine RTF 
source code in individual files into one larger RTF file.

@@

>>>>

```{r}
tlf_path <- c(
  "tlf/tbl_disp.rtf",  # Disposition Table 
  "tlf/tlf_eff.rtf",   # Efficacy Table
  "tlf/tlf_km.rtf"     # KM Plot 
)
```

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf-combine.pdf")
```

@@

```{r, include=FALSE}
#' Assemble RTF files into one single RTF file 
#' 
#' @param path a vector of RTF file path
#' 
#' @export
rtf_assemble <- function(path){

  rtf <- lapply(path, readLines)

  n <- length(rtf)
  start <- c(1, rep(2, n - 1))
  end <- vapply(rtf, length, numeric(1))
  end[-n] <- end[-n] - 1

  for(i in 1:n){
    rtf[[i]] <- rtf[[i]][start[i]:end[i]]
    if(i < n) rtf[[i]] <- c(rtf[[i]], r2rtf:::as_rtf_new_page())
  }
  rtf <- do.call(c, rtf)

  rtf

}
```

The `rtf_assemble()` function allow you to combine RTF 
source code in individual files into one larger RTF file.

@@

```{r}
rtf_assemble(tlf_path) |> 
  r2rtf::write_rtf("tlf/rtf-combine.rtf")
```
